Weighted Model Counting with Conditional Weights

### 2020-08-05 paper/paper.tex
Proof of theorem 2

\usepackage{amsthm}
\usepackage{thmtools,thm-restate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{complexity}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[binary-units]{siunitx}
\usepackage[inline]{enumitem}
\usetikzlibrary{cd}
\usetikzlibrary{bayesnet}
\usetikzlibrary{calc}
\DeclareMathOperator{\im}{im}
\newtheorem{theorem}{Theorem}
\newtheorem{observation}{Observation}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

Introduce WMC \cite{DBLP:conf/aaai/SangBK05}

@@

% TODO: introduce this section and explain why there's so much about BNs
A Bayesian network is a directed acyclic graph with random variables as vertices
that defines a probability distribution over them. The full probability
distribution can be expressed as the product of the conditional probability
distributions of all random variables. For discrete Bayesian networks (and we
only consider discrete networks in this paper), each such distribution can be
represented by a table known as a conditional probability table (CPT).

@@

\paragraph{ADDs and their use in probabilistic inference.} ADDs provide an
efficient way to manipulate functions from a Boolean algebra to any algebraic
structure (most commonly the real numbers)
\cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been used to represent value
functions in Markov decision processes \cite{DBLP:conf/uai/HoeySHB99} and, for
Bayesian network inference, to represent each CPT as an ADD
\cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and arithmetic
circuits into a  single representation \cite{DBLP:conf/ijcai/ChaviraD07}. ADDs
are particularly advantageous in this situation because of their ability to
fully exploit context-specific independence, i.e., observable structure within a
CPT that is not inherited from the structure of the Bayesian network
\cite{DBLP:conf/uai/BoutilierFGK96}.

@@

Let $\mathcal{L}$ be a propositional logic with atoms $a$ and $b$, and let $U =
\{ a, b \}$. Then $2^U$, the power set of $U$, is the set of all models of
$\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets can also be
represented as Boolean algebras (e.g., $(2^{2^U}, \land, \lor, \neg, \bot,
\top)$)---see \cref{tbl:notation_example} for examples of how various elements
can be represented in both notations. Most importantly, note that the word
\emph{atom} has completely different meanings in logic and in Boolean algebras.
An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of $U$, whereas
an atom in a Boolean algebra is (in set-theoretic terms) a singleton set. For
instance, an atom in $2^{2^U}$ corresponds to a model of $\mathcal{L}$, i.e., an
element of $2^U$. Unless referring specifically to a logic, we will use the
algebraic definition of an atom while referring to logical atoms as
\emph{variables}. In the rest of the paper, for any set $U$, we will use
set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
model $x \in 2^U$.

@@

We build on the definitions of multiplication and projection in the ADDMC paper
\cite{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
manipulate functions from Boolean algebras to non-negative real numbers. All of
these operations have efficient implementations in the CUDD
\cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
is used by ADDMC {\cite{DBLP:conf/aaai/DudekPV20}.

@@

\begin{restatable}{theorem}{extendable}
  For any set $U$ and measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$, there
  exists a set $V \supseteq U$ and a factorable measure $\mu'\colon 2^{2^V} \to
  \mathbb{R}_{\ge 0}$ such that $\mu = \mu' \circ \iota$, where $\iota\colon
  2^{2^U} \to 2^{2^V}$ is the inclusion homomorphism.
\end{restatable}

@@

In this section, we describe a way to encode Bayesian networks into WMC without
restricting oneself to factorable measures and thus having to add extra
variables to maintain literal independence. In line with the names of previous
encodings, we shall call this encoding \texttt{db21}. Recall that a Bayesian
network is a directed acyclic graph with random variables as vertices. Let
$\mathcal{V}$ denote the set of random variables. For any random variable $X \in
\mathcal{V}$, let $\im X$ denote its set of possible values and $\mathrm{pa}(X)$
the set of its parents. The full probability distribution is then equal to
$\prod_{X \in \mathcal{V}} \Pr(X \mid \mathrm{pa}(X))$. See
\cref{fig:example_bn} for an example Bayesian network which we will refer to
throughout this section. For this network, $\mathcal{V} = \{ W, F, T \}$,
$\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W \}$, $\im
W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.

@@

For the Bayesian network in \cref{fig:example_bn}, this gives us:
\begin{align*}
  \mathcal{E}(W) &= \{ \lambda_{W=1} \}, \\
  \mathcal{E}(F) &= \{ \lambda_{F=1} \}, \\
  \mathcal{E}(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h} \}, \\
  \mathcal{E}^*(W) &= \{ \lambda_{W=1} \}, \\
  \mathcal{E}^*(F) &= \{ \lambda_{F=1}, \lambda_{W=1} \}, \\
  \mathcal{E}^*(T) &= \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h}, \lambda_{W=1} \}.
\end{align*}

\begin{algorithm}
  \caption{Encoding a Bayesian network}
  \label{alg:encoding}
  \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
  \KwResult{a function $\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
  $\phi \gets 1$\;
  \For{$X \in \mathcal{V}$}{
    \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
    $\mathrm{CPT}_X \gets 0$\;
    \eIf{$|\im X| = 2$}{
      \For{$(y_1, \dots, y_n) \in \prod_{i = 1}^n \im Y_i$}{
        $p_1 \gets \Pr(X = 1 \mid y_1, \dots, y_n)$\;
        $p_0 \gets \Pr(X \ne 1 \mid y_1, \dots, y_n)$\;
        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_1[\lambda_{X=1}] \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + p_0 \overline{[\lambda_{X=1}]} \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
      }
    }{
      \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
      \For{$x \in \im X$ {\rm \textbf{and}} $(y_1, \dots, y_n) \in \prod_{i =
          1}^n \im Y_i$}{
        $p_x \gets \Pr(X = x \mid y_1, \dots, y_n)$\;
        $\mathrm{CPT}_X \gets \mathrm{CPT}_X + p_x[\lambda_{X=x}] \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}] + \overline{[\lambda_{X=1}]} \cdot
        \prod_{i=1}^n [\lambda_{Y_i=y_i}]$\;
      }
      $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m [\lambda_{X
          = x_i}] \right) \cdot \prod_{i=1}^m \prod_{j=i+1}^m
      (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})$\;
    }
    $\phi \gets \phi \cdot \mathrm{CPT}_X$\;
  }
  \Return{$\phi$}\;
\end{algorithm}

@@

For a binary random variable $X$, $\mathrm{CPT}_X$ is simply a sum of smaller
functions, one for each row of the CPT. If $X$ has more than two values, we also
multiply $\mathrm{CPT}_X$ by some `clause' functions that restrict the value of
$\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$. For the Bayesian
network in \cref{fig:example_bn}, we get:
\begin{align*}
  \mathrm{CPT_W} &= 0.5[\lambda_{W=1}]+0.5\overline{[\lambda_{W=1}]} = 0.5 \cdot 1, \\
  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] \\
                 &+ 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}] \\
                 &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4\overline{[\lambda_{F=1}]} \cdot [\lambda_{W=1}] \\
                 &+ 0.1[\lambda_{F=1}] \cdot \overline{[\lambda_{W=1}]} + 0.9\overline{[\lambda_{F=1}]} \cdot \overline{[\lambda_{W=1}]}, \\
  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \\
                 &\cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \\
                 &\cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot (\dots).
\end{align*}

@@

% TODO: To follow formatting requirements, I will need to remove the
% nput command. Each figure will have to be separately compiled to a PDF (maybe
% create a Makefile for that).
% TODO: look up how to scale figures
% TODO: reformat all colours to CMYK from RGB (in R)

@@

\extendable*
\begin{proof}
  TODO
\end{proof}

@@

\correctness*
\begin{proof}
  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
  \begin{align*}
    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) \\
                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) \\
                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
                                                        &= \sum_{(y_i)_{i=1}^n \in \prod_{i=1}^n \im Y_i} \Pr(x, y_1, \dots, y_n) \\
                                                        &= \Pr(X = x)
  \end{align*}
  by the following arguments:
  \begin{itemize}
  \item the proof of Theorem~1 in the ADDMC paper \cite{DBLP:conf/aaai/DudekPV20};
  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
  \item \cref{lemma:full_distribution};
  \item marginalisation of a probability distribution.
  \end{itemize}
\end{proof}
% TODO: need to make the proof nicer.

>>>>

\usepackage{amsthm}
\usepackage{thmtools,thm-restate}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage{complexity}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[binary-units]{siunitx}
\usepackage[inline]{enumitem}
\usetikzlibrary{cd}
\usetikzlibrary{bayesnet}
\usetikzlibrary{calc}
\DeclareMathOperator{\im}{im}
\newtheorem{theorem}{Theorem}
\newtheorem{observation}{Observation}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\makeatletter
\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
\newcommand{\pushline}{\Indp}% Indent
\newcommand{\popline}{\Indm\dosemic}% Undent
\makeatother

@@

% TODO
Introduce WMC \cite{DBLP:conf/aaai/SangBK05}

@@

@@

\paragraph{ADDs and their use in probabilistic inference.} ADDs provide an
efficient way to manipulate functions from a Boolean algebra to any algebraic
structure (most commonly the real numbers)
\cite{DBLP:journals/fmsd/BaharFGHMPS97}. They have been used to represent value
functions in Markov decision processes \cite{DBLP:conf/uai/HoeySHB99} and, for
Bayesian network inference, to represent each conditional probability table
(CPT) as an ADD \cite{DBLP:conf/icml/ZhaoMP15} as well as by combining ADDs and
arithmetic circuits into a  single representation
\cite{DBLP:conf/ijcai/ChaviraD07}. ADDs are particularly advantageous in this
situation because of their ability to fully exploit context-specific
independence, i.e., observable structure within a CPT that is not inherited from
the structure of the Bayesian network \cite{DBLP:conf/uai/BoutilierFGK96}.

@@

Let $\mathcal{L}$ be a propositional logic with atoms $a$ and $b$, and let $U =
\{ a, b \}$. Then $2^U$, the power set of $U$, is the set of all models of
$\mathcal{L}$, and $2^{2^U}$ is the set of all formulas. These sets can also be
represented as Boolean algebras (e.g., $(2^{2^U}, \land, \lor, \neg, \bot,
\top)$) with a partial order $\le$ that corresponds to set inclusion
$\subseteq$---see \cref{tbl:notation_example} for examples of how various
elements can be represented in both notations. Most importantly, note that the
word \emph{atom} has completely different meanings in logic and in Boolean
algebras. An atom in $\mathcal{L}$ is an atomic formula, i.e., an element of
$U$, whereas an atom in a Boolean algebra is (in set-theoretic terms) a
singleton set. For instance, an atom in $2^{2^U}$ corresponds to a model of
$\mathcal{L}$, i.e., an element of $2^U$. Unless referring specifically to a
logic, we will use the algebraic definition of an atom while referring to
logical atoms as \emph{variables}. In the rest of the paper, for any set $U$, we
will use set-theoretic notation for $2^U$ and Boolean-algebraic notation for
$2^{2^U}$, except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$
for some model $x \in 2^U$.

@@

We build on the definitions of multiplication and projection by
\citet{DBLP:conf/aaai/DudekPV20} and define more operations that can be used to
manipulate functions from Boolean algebras to non-negative real numbers. All of
these operations have efficient implementations in the CUDD
\cite{somenzi1998cudd} package for manipulating ADDs (among other things) that
is used by ADDMC {\cite{DBLP:conf/aaai/DudekPV20}.

@@

\begin{restatable}{theorem}{extendable}
  For any set $U$ and measure $\mu\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$, there
  exists a set $V \supseteq U$, a factorable measure $\mu'\colon 2^{2^V} \to
  \mathbb{R}_{\ge 0}$, and a formula $f \in 2^{2^V}$ such that $\mu(x) = \mu'(x
  \land f)$ for all formulas $x \in 2^{2^U}$.
\end{restatable}

@@

In this section, we describe a way to encode Bayesian networks into WMC without
restricting oneself to factorable measures and thus having to add extra
variables to maintain literal independence. In line with the names of previous
encodings, we shall call this encoding \texttt{db21}.

A Bayesian network is a directed acyclic graph with random variables as vertices
that defines a probability distribution over them. Let $\mathcal{V}$ denote this
set of random variables. For any random variable $X \in \mathcal{V}$, let $\im
X$ denote its set of values and $\mathrm{pa}(X)$ its set of parents. The
full probability distribution is then equal to $\prod_{X \in \mathcal{V}} \Pr(X
\mid \mathrm{pa}(X))$. For discrete Bayesian networks (and we only consider
discrete networks in this paper), each factor of this product can be represented
by a CPT. See \cref{fig:example_bn} for an example Bayesian network which we
will refer to throughout this section. For this network, $\mathcal{V} = \{ W, F,
T \}$, $\mathrm{pa}(W) = \emptyset$, $\mathrm{pa}(F) = \mathrm{pa}(T) = \{ W
\}$, $\im W = \im F = \{0, 1 \}$, and $\im T = \{ l, m, h \}$.

@@

For example, in the Bayesian network from \cref{fig:example_bn},
$\mathcal{E}^*(T) = \{ \lambda_{T=l}, \lambda_{T=m}, \lambda_{T=h},
\lambda_{W=1} \}$.

\begin{algorithm}
  \caption{Encoding a Bayesian network}
  \label{alg:encoding}
  \KwData{vertices $\mathcal{V}$, probability distribution $\Pr$}
  \KwResult{$\phi\colon 2^U \to \mathbb{R}_{\ge 0}$}
  $\phi \gets 1$\;
  \For{$X \in \mathcal{V}$}{
    \textit{let} $\mathrm{pa}(X) = \{ Y_1, \dots, Y_n \}$\;
    $\mathrm{CPT}_X \gets 0$\;
    \eIf{$|\im X| = 2$}{
      \For{$(y_i)_{i=1}^n \in \prod_{i = 1}^n \im Y_i$}{
        $p_1 \gets \Pr(X = 1 \mid y_1, \dots, y_n)$\;
        $p_0 \gets \Pr(X \ne 1 \mid y_1, \dots, y_n)$\;
        \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X$\;
        \pushline $+ p_1[\lambda_{X=1}] \cdot \prod_{i=1}^n
        [\lambda_{Y_i=y_i}]$\;
        \dosemic $+ p_0 \overline{[\lambda_{X=1}]} \cdot \prod_{i=1}^n
        [\lambda_{Y_i=y_i}]$\;
      }
    }{
      \textit{let} $\im X = \{ x_1, \dots, x_m \}$\;
      \For{$x \in \im X$ {\rm \textbf{and}} $(y_i)_{i=1}^n \in \prod_{i = 1}^n
        \im Y_i$}{
        $p_x \gets \Pr(X = x \mid y_1, \dots, y_n)$\;
        \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X$\;
        \pushline $+ p_x[\lambda_{X=x}] \cdot \prod_{i=1}^n
        [\lambda_{Y_i=y_i}]$\;
        \dosemic $+ \overline{[\lambda_{X=x}]} \cdot \prod_{i=1}^n
        [\lambda_{Y_i=y_i}]$\;
      }
      \nosemic $\mathrm{CPT}_X \gets \mathrm{CPT}_X \cdot \left( \sum_{i=1}^m
        [\lambda_{X = x_i}] \right)$\;
      \pushline\dosemic $\cdot \prod_{i=1}^m \prod_{j=i+1}^m
      (\overline{[\lambda_{X = x_i}]} + \overline{[\lambda_{X = x_j}]})$\;
    }
    $\phi \gets \phi \cdot \mathrm{CPT}_X$\;
  }
  \Return{$\phi$}\;
\end{algorithm}

@@

For a binary random variable $X$, $\mathrm{CPT}_X$ is simply a sum of smaller
functions, one for each row of the CPT. If $X$ has more than two values, we also
multiply $\mathrm{CPT}_X$ by some `clause' functions that restrict the value of
$\phi(T)$ to zero whenever $|\mathcal{E}(X) \cap T| \ne 1$. For the Bayesian
network in \cref{fig:example_bn}, we get:
\begin{align*}
  \mathrm{CPT_F} &= 0.6[\lambda_{F=1}] \cdot [\lambda_{W=1}] + 0.4[\lambda_{F=0}] \cdot [\lambda_{W=1}] \\
                 &+ 0.1[\lambda_{F=1}] \cdot [\lambda_{W=0}] + 0.9[\lambda_{F=0}] \cdot [\lambda_{W=0}], \\
  \mathrm{CPT_T} &= ([\lambda_{T=l}] + [\lambda_{T=m}] + [\lambda_{T=h}]) \\
                 &\cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=m}]}) \cdot (\overline{[\lambda_{T=l}]} + \overline{[\lambda_{T=h}]}) \\
                 &\cdot (\overline{[\lambda_{T=m}]} + \overline{[\lambda_{T=h}]}) \cdot \dots.
\end{align*}

@@

% TODO: To follow formatting requirements, I will need to remove the
% nput command. Each figure will have to be separately compiled to a PDF (maybe
% create a Makefile for that). Look up how to scale figures. Reformat all
% colours to CMYK from RGB (in R).

@@

\extendable*
\begin{proof}
  Let $V = U \cup \{ f_m \mid m \in 2^U \}$, and $f = \bigwedge_{m \in 2^U} \{ m
  \} \leftrightarrow f_m$. We define weight function $\nu\colon 2^V \to
  \mathbb{R}_{\ge 0}$ as $\nu = \prod_{v \in V} \nu_v$, where $\nu_v(\{v\}) =
  \mu(\{m\})$ if $v = f_m$ for some $m \in 2^U$ and $\nu_v(x) = 1$ for all other
  $v \in V$ and $x \in 2^{\{v\}}$. Let $\mu'\colon 2^{2^V} \to \mathbb{R}_{\ge
    0}$ be the measure induced by $\nu$. It is enough to show that $\mu$ and $x
  \mapsto \mu'(x \land f)$ agree on the atoms in $2^{2^U}$. For any $\{ a \} \in
  2^{2^U}$,
  \begin{align*}
    \mu'(\{ a \} \land f) &= \sum_{\{ x \} \le \{ a \} \land f} \nu(x) = \nu(a \cup \{ f_a \}) \\
                          &= \nu_{f_a}(\{ f_a \}) = \mu(\{ a \})
  \end{align*}
  as required.
\end{proof}

@@

\correctness*
\begin{proof}
  Let $\mathcal{V} = \{ X, Y_1, \dots, Y_n \}$. Then
  \begin{align*}
    (\exists_U (\phi \cdot [\lambda_{X=x}]))(\emptyset) &= \sum_{T \in 2^U} (\phi \cdot [\lambda_{X=x}])(T) \\
                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \phi(T) \\
                                                        &= \sum_{\lambda_{X=x} \in T \in 2^U} \left( \prod_{Y \in \mathcal{V}} \mathrm{CPT}_Y \right)(T) \\
                                                        &= \sum_{(y_i)_{i=1}^n \in \prod_{i=1}^n \im Y_i} \Pr(x, y_1, \dots, y_n) \\
                                                        &= \Pr(X = x)
  \end{align*}
  by the following arguments:
  \begin{itemize}
  \item the proof of Theorem~1 by \citet{DBLP:conf/aaai/DudekPV20};
  \item if $\lambda_{X=x} \not\in T \in 2^U$, then $(\phi \cdot
    [\lambda_{X=x}])(T) = \phi(T) \cdot [\lambda_{X=x}](T \cap \{
    \lambda_{X=x} \}) = \phi(T) \cdot 0 = 0$;
  \item \cref{lemma:full_distribution};
  \item marginalisation of a probability distribution.
  \end{itemize}
\end{proof}
% TODO: need to make the proof nicer.
